An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-05-15 paper.tex
Wording tweaks

    To measure the source of scheduler duration jitter, We created additional work-load, executing alone with
    cyclictest, with FIFO scheduling policy and highest priority in Cyclone V based system, during profiling session. We
    created a overloaded condition, which has 8 stress threads, doing either CPU, memory or I/O bounded task. The
    scheduler duration of cyclictest real-time task under each type of loading condition is shown in figure
    \ref{fig:sd_cpu}, \ref{fig:sd_memory}, and \ref{fig:sd_io}. This result exhibits a mostly static scheduler
    duration with seldom jitter with maximum of 20us in CPU and I/O bounded loads. But putting the system in to heavy
    memory loading condition, the result, shown in figure \ref{fig:sd_memory} shows an increased average of scheduler
    duration and exhibits random jitter up to 34us. The spread of distribution of scheduler duration would also become
    wilder. This informs us that the scheduler duration is not a static value and will increase alone with the system's
    load, especially memory related load. This informs that the scheduler runnable task selection process execution time
    could be lengthen by user-space task, doing memory bounded tasks.

@@

    To mitigate the influence of memory bounded tasks, we isolated the real-time task into dedicated CPU core, and
    pinned memory bounded tasks to another CPU core. In addition, we make the shared L2 cache only accessible from the
    CPU core, running real-time task. The result of scheduler duration in shown in figure \ref{fig:sd_iso}. The
    scheduler duration is stabilized and showing as distribution as other loading conditions. The stress memory bounded
    tasks were designed to spin on malloc and free calls. This suggests us that memory allocation and deallocation would
    decrease the scheduler performance and increase its execution jitter via cache and memory model. Also, we gathered
    the result of pining both real-time and loads to same CPU core. Figure \ref{fig:sd_same_no_cache} shows the result
    of running on CPU core without L2 cache.  Comparing with figure \ref{fig:sd_memory}, result under 2 core SMP, this
    result showns a slight improvement of average latency and jitter. This informs that shared L2 cache and dynamic
    number of loading tasks, sharing CPU with real-time task, would be the source of scheduler duration jitter. Thus,
    decrease the use of dynamic memory allocation, real-time task CPU isolation and cache lockdown could prevent raising
    the scheduler duration, keeping it as a stable value, about 10us.

>>>>

    To measure the source of scheduler duration jitter, We created additional work-load, executing alone with
    cyclictest, with FIFO scheduling policy and highest priority in Cyclone V based system, during profiling session. We
    created a overloaded condition, which has 8 stress threads, doing either CPU, memory or I/O bounded task. The
    scheduler duration of cyclictest real-time task under each type of loading condition is shown in figure
    \ref{fig:sd_cpu}, \ref{fig:sd_memory}, and \ref{fig:sd_io}. This result exhibits a mostly static scheduler
    duration with seldom jitter with maximum of 20us in CPU and I/O bounded loads. But putting the system in to heavy
    memory loading condition, the result, shown in figure \ref{fig:sd_memory} shows an increased average of scheduler
    duration and exhibits random jitter up to 34us. The spread of distribution of scheduler duration would also become wilder, that implies scheduler duration is not a static value and will increase alone with the system load, especially memory related load.
    Therefore, the scheduler runnable task selection process execution time
    could be lengthen by user-space task, doing memory bounded tasks.

@@

    To mitigate the influence of memory bounded tasks, we isolated the real-time task into dedicated CPU core, and
    pinned memory bounded tasks to another CPU core. In addition, we make the shared L2 cache only accessible from the
    CPU core, running real-time task. The result of scheduler duration in shown in figure \ref{fig:sd_iso}. The
    scheduler duration is stabilized and showing as distribution as other loading conditions. The stress memory bounded
    tasks were designed to spin on malloc and free calls. This suggests us that memory allocation and deallocation would
    decrease the scheduler performance and increase its execution jitter via cache and memory model. Also, we gathered
    the result of pining both real-time and loads to same CPU core.

    Figure \ref{fig:sd_same_no_cache} shows the result
    of running on CPU core without L2 cache.  Comparing with figure \ref{fig:sd_memory}, result under 2 core SMP, this
    result showns a slight improvement of average latency and jitter, that means shared L2 cache and dynamic
    number of loading tasks, sharing CPU with real-time task, would be the source of scheduler duration jitter. Thus,
    decrease the use of dynamic memory allocation, real-time task CPU isolation and cache lockdown could prevent raising
    the scheduler duration, keeping it as a stable value, about 10us.
